Converging High-Throughput and High-Performance Computing Paradigms: \\ A Case Study of Using Abstractions to Bridge the Divide

### 2017-03-12 PandaEvolution.tex

Compared to pilots, backfill has the disadvantage of limiting the amount of work
nodes that can be requested. Pilots are normal jobs: they can request as many
work nodes for as much time as a queue can offer. On the contrary, jobs sized on
the base of the backfill availability depend on the
% amount of work nodes that cannot be given to any other job.
any other job in the Titan's queue\sergeynote{any other job currently in the
Titan's queue?}\mtnote{Better?}. Usually, backfill availability is a fraction of
the total capacity of the queue but the size of Titan mitigates this limitation.
Every year, about 10\% of Titan's capacity remains
unused~\cite{titan_utilization}, for a total of 30,000 cores, corresponding to
around 270M core hours per year, roughly 30\% of the overall capacity of WLCG.

>>>>

Compared to pilots, backfill has the disadvantage of limiting the amount of
work nodes that can be requested. Pilots are normal jobs: they can request as
many work nodes for as much time as a queue can offer. On the contrary, jobs
sized on the basis of backfill information availability \jhanote{should be
resource availability or backfill queue information?} depend on the % amount
of work nodes that cannot be given to any other job. any other job in the
Titan's queue\sergeynote{any other job currently in the Titan's
queue?}\mtnote{Better?}. Usually, backfill availability is a fraction of the
total capacity of the queue but the size of Titan mitigates this limitation.
Every year, about 10\% of Titan's capacity remains
unused~\cite{titan_utilization}, corresponding to an average of 30,000 unused
cores. This equals approximately 270M core hours per year, roughly 30\% of the
overall capacity of WLCG.
